Detecting the impact of land cover change on observed rainfall.

### 2019-03-14 Manuscripts/PeerJRainfall_Landuse/Rainfall_Landuse.tex
Update files for change to png
Upload since push does not work?

\begin{abstract}
Analysis of observational data to pinpoint impact of land cover change
on local rainfall are difficult due to multiple environmental factors
that cannot be strictly controlled. In this study we use a statistical
approach to identify the relationship between removal of tree cover and
rainfall with data from best available sources for two large areas in
Australia. Gridded rainfall data between 1979 and 2015 was used for the
areas, while large scale (exogenous) effects were represented by mean
rainfall across a much larger area and climatic indicators, such as SOI
and IOD. Both general additive modelling and step trend tests were used
for the analysis. For a region in south central Queensland, the reported
change in tree clearing between 2002 - 2005 did not result in strong
statistically significant precipitation changes. On the other hand,
results from a bushfire affected region on the border of New SOuth Wales
and Victoria suggests significant changes in the rainfall due to changes
in tree cover. This indicates the method works better when a abrupt
change in the data can be clearly identified. The results from the step
trend test also mainly identified a positive relationship between the
tree cover and the rainfall at p \textless{} 0.1 at the NSW/Victoria
region. High rainfall variability and possible regrowth could have
impacted the results in the Queensland region.
% Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

@@

\caption{\label{tab:Zscore}The interpretation of Z' score in the step trend test}
\centering
\begin{tabular}{l}
\toprule
 \\
\midrule
\$Z'>0\$  and rainfall decreases after change\\
\$Z'<0\$ and rainfall increases post change\\
\$Z'=0\$ and rainfall does not change\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth,height=0.7\textheight]{figures/soi_explhistogram} \caption{The performance of the regression model if rainfall is only modelled by the climate drivers. It shows the percentage of rainfall variability that can be explained by the climate drivers for the Qld and NSW/VIC region}\label{fig:rsq}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth,height=0.7\textheight]{figures/ResidualBoxplotchange} \caption{Boxplots of annual rainfall residuals (estimated based on Equation 2 before and after the land cover intervention during 1979 - 2015 in the study regions. On average, the after period has a significantly lower annual rainfall residual in NSW/VIC, but a signifcantly higher annual rainfall residual in the Qld study area}\label{fig:meandiff}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth]{figures/bt4_hist} \caption{Field significance results showing the distribution of percentage of significant $Z'$ scores for the resampled series (blue bars), and the precentage significant $Z'$ scores for the original series of rainfall years (red circle)}\label{fig:fieldsig}
\end{figure}

>>>>

\begin{abstract}
Analysis of observational data to pinpoint impact of land cover change
on local rainfall are difficult due to multiple environmental factors
that cannot be strictly controlled. In this study we use a statistical
approach to identify the relationship between removal of tree cover and
rainfall with data from best available sources for two large areas in
Australia. Gridded rainfall data between 1979 and 2015 was used for the
areas, while large scale (exogenous) effects were represented by mean
rainfall across a much larger area and climatic indicators, such as
Southern Oscillation Index and Indian Ocean Dipole. Both general
additive modelling and step trend tests were used for the analysis. For
a region in south central Queensland, the reported change in tree
clearing between 2002 - 2005 did not result in strong statistically
significant precipitation changes. On the other hand, results from a
bushfire affected region on the border of New South Wales and Victoria
suggests significant changes in the rainfall due to changes in tree
cover. This indicates the method works better when a abrupt change in
the data can be clearly identified. The results from the step trend test
also mainly identified a positive relationship between the tree cover
and the rainfall at p \textless{} 0.1 at the NSW/Victoria region. High
rainfall variability and possible regrowth could have impacted the
results in the Queensland region.
% Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

@@

\caption{\label{tab:Zscore}The interpretation of Z' score in the step trend test}
\centering
\begin{tabular}{l}
\toprule
 \\
\midrule
$Z'>0$  and rainfall decreases after change\\
$Z'<0$ and rainfall increases post change\\
$Z'=0$ and rainfall does not change\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth]{figures/soi_explhistogram} \caption{The performance of the regression model if rainfall is only modelled by the climate drivers. It shows the percentage of rainfall variability that can be explained by the climate drivers for the Qld and NSW/VIC region}\label{fig:rsq}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth]{figures/ResidualBoxplotchange} \caption{Boxplots of annual rainfall residuals (estimated based on Equation 2 before and after the land cover intervention during 1979 - 2015 in the study regions. On average, the after period has a significantly lower annual rainfall residual in NSW/VIC, but a signifcantly higher annual rainfall residual in the Qld study area}\label{fig:meandiff}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.7\linewidth]{figures/bt4_hist} \caption{Field significance results showing the distribution of percentage of significant Z' scores for the resampled series (blue bars), and the precentage significant Z' scores for the original series of rainfall years (red circle)}\label{fig:fieldsig}
\end{figure}
